---
title: "R - Assignment Mod 2 Week 2"
author: "Nusrat J Prithee"
date: "01-28-2022"
output:
  html_document:default
---




```{r setup, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
# knitr::opts_chunk$set(include = F)
# knitr::opts_chunk$set(echo = TRUE)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```



# HW - Module 2 week 02

## Q1. 
Read in the file with all the baseball players height, weight and age info (BaseballHeightWeight.csv) as a dataframe and save it as baseball. Then display the structure of the dataframe.

```{r Q1, echo=FALSE, warning=TRUE}

baseball<-data.frame(read.csv("BaseballHeightWeight.csv"))
str(baseball)
```
 Here in out put find 1034 objects and 6 variables are showed. Height.inches, weight.pounds are integer variable, Age is number, Name,Team,Position are char variable. read() function read data from cvs file. str() function provid the structure of baseball object.

## Q2. 
print out the first 5 and the last 3 rows of the dataframe

```{r Q2, echo=FALSE, warning=TRUE}
head(baseball,n=5)
tail(baseball,n=3)
```
head() function use to get first 5 rows of the table,tail() function use to get last 3 rows from the table.
## Q3. 
Change the headers/column names from Weight.pounds. to weight, from Height.inches. to height, and Age to age.

```{r Q3, warning=TRUE}
colnames(baseball)[4:6]=c("height","weight","age")
```
No output will be shown. It will change the name of column4 to Column6 from data table.
## Q4. 
Print out the first two lines again to see the new column names.
```{r Q4, echo=FALSE, warning=TRUE}
head(baseball,n=2)

```
New column names are found in output.
## Q5. 
Find the statistics (summary) of the heights, weights, and ages of the players. Using complete sentences, give the reader these summary.
```{r Q5, echo=FALSE, warning=TRUE}
summary(baseball$height)
summary(baseball$weight)
summary(baseball$age)


```
Summary() function provids the statistics of three variables. Min,Max,Mean, Median ,1st Qu., 2nd Qu is shown as an output.And weight data shows NA value.

## Q6. 
You should find an issue with the weight data with an NA value. Use the subset( ) function, select that data point (save as shyboy) and find out who the shy boy was.
```{r Q6, echo=FALSE, warning=TRUE}
shyboy= subset(baseball,is.na(weight))
str(shyboy)

```
Here subset() shows the row in output where weight has NA value.  
## Q7. 
Remove shyboy from baseball, and then show the number of observations of the cleaned up dataframe baseball.
```{r Q7, message=TRUE, warning=TRUE}
baseball= subset(baseball,weight>0)
str(baseball)

```
There are 1033 object found after removing NA value.

## Q8. 
Make a quick boxplot of the weight of the players. Use the title( ) function immediately to add a title to the chart. (Try color #0000FF for blue.)
```{r Q8, echo=FALSE, warning=TRUE}
boxplot(baseball$weight,main="Baseball player weight boxplot",ylab="weight(lbs)",col = '#0000FF')

```

main is used to give the title, ylab is for lebel y axis and color.   blue box is found in output. 
## Q9. 
Make a histogram of the weight of the players. Try color 'green' this time. The function understands the word 'green' just fine. Give it a better title than the default. Does the distribution looks normal?
```{r Q9, echo=FALSE, warning=TRUE}
hist(baseball$weight,main = "Histogram of baseball player weight",col = ('green'))

```
histogram looks like a bell shape. 

## Q10. 
Use ggplot, make a plot with weights vs heights of the players, color by Teams. Give it an appropriate title.
```{r Q10, echo=FALSE, warning=TRUE}
library("ggplot2")
ggplot(data=baseball)+ 
  geom_point(mapping=aes(x=height,y=weight,color=Team))+
  ggtitle("Scatter plot of baseball player weight(y) vs height(x)")

```
geom_point() function is used to create scatterplotss. Weight is in Y axis, height is in x axis. team is represented by color.
## Q11. 
Make a plot with weights vs heights of the players, color by age
```{r Q11, echo=FALSE, warning=TRUE}
library("ggplot2")
ggplot(data=baseball)+ 
  geom_point(mapping=aes(x=height,y=weight,color=age))+
  ggtitle("Scatter plot of baseball player weight(y) vs height(x)")

```
Age has numeric value. Color has changed due to numeric value.

## Q12. 
Obtain a subset of the data with only Team Washington. Using complete sentences, give the number of players in Team Washington.
```{r Q12, echo=FALSE, warning=TRUE}
teamwash <- subset(baseball,Team =='WAS')
str(teamwash)

```

There are 36 player in team Washington.
## Q13. 
Obtain another subset with Team Washington and only players older than 28. How many are there in this veteran group?
```{r Q13, echo=FALSE, message=TRUE, warning=TRUE, paged.print=FALSE}
teamwash <- subset(baseball,Team =='WAS' & age>28)
str(teamwash)

```

There are 14 player older than 28 in team Washington.
